% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{makecell}
% \usepackage{fancyhdr}
% \pagestyle{fancy}

\usepackage{multicol}


% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Michael W. Davidson\\
\emph{\normalsize{PhD Student}}}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://pages.ucsd.edu/~mwdavids/docs/cv.pdf}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor=[rgb]{0,0.2,.6},
  pdfauthor = {\name},
  pdfkeywords = {political science, statistics, networks, corruption, clientelism, political parties, data science},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}
\vspace{.5em}
% \Xhline{2\arrayrulewidth}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.5em}

\begin{minipage}{0.45\linewidth}
  \href{http://www.ucsd.edu}{University of California, San Diego} \\
  Department of Political Science \\
  347 Social Science Building \\
  La Jolla, CA 92093-0502
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (470) 955-7835 \\
    Email: & \href{mailto:mwdavidson@ucsd.edu}{\tt mwdavidson@ucsd.edu} \\
    Homepage: & \href{http://pages.ucsd.edu/~mwdavids/}{\tt http://pages.ucsd.edu/mwdavids/} \\
  \end{tabular}
\end{minipage}


\section*{Education}

\begin{itemize}
\item Doctorate of Philosophy, University of California, San Diego, \emph{anticipated 2017} 

  \item Bachelor of Arts, Political Science, Brigham Young University, 2011


\end{itemize}

\section*{Publications}

% \subsection*{Journal Articles}

% \begin{enumerate}
% \item A General Mathematical Theory of Depreciation, 1929, {\it Journal
%     of The American Statistical Association} 20, 340--353.
% \item Differential Equations Subject to Error, 1927, {\it Journal of The
%     American Statistical Association}.
% \item Applications of the Theory of Error to the Interpretation of
%   Trends (with H. Working), 1929, {\it Journal of the American
%     Statistical Association}.
% \end{enumerate}

% \subsection*{Proceedings}

% \begin{enumerate}
% \item ``Inter-ethnic Civic Engagement and Discrimination'', with Joel
%   S. Selway. Presented at the 2011 American Political Science Association
%   Annual Conference in Seattle,
%   WA.

% \item  ``Democracy and Diversity Revisited''. Presented at the 2013
%   Center for Democracy's Graduate Student Conference. Irvine, CA.
% \end{enumerate}

\subsection*{Peer-Reviewed Articles}
\begin{enumerate}
\item ``Using Networks to Combine `Big Data' and Traditional Surveillance to Improve Influenza Predictions.''  2015. Michael W. Davidson, Dotan A. Haim and Jennifer Radin.
\href{http://www.nature.com/srep/2015/150129/srep08154/full/srep08154.html}{Scientific Reports} 5 (8154): 1-5.
\end{enumerate}

\subsection*{Other Articles}
\begin{enumerate}
\item ``Local Machines and Vote Brokerage in the Philippines.'' 2016. Edward Aspinall, Michael W. Davidson, Allen Hicken and Meredith L. Weiss. \href{https://muse.jhu.edu/article/628451/summary}{Contemporary Southeast Asia: A Journal of International and Strategic Affairs} 38 (2): 191-196.
\end{enumerate}

\subsection*{Under Review}
\begin{enumerate}
  \item ``Prenatal Sex Hormones and Social Integration'' with \href{https://sites.google.com/site/webpagesjaromir/}{Jarom\'{i}r Kov\'{a}\v{r}\'{i}k},
\href{https://sites.google.com/site/pablobranasgarza/home}{Pablo Bra\~{n}as-Garza}, Shannon Carcelli, Dotan A. Haim and \href{jhfowler.ucsd.edu}{James H. Fowler}. \emph{R\&R} 

\item ``Family Networks, Clientelism, and Voter Bahavior: Evidence from the Philippines'' with \href{http://www.allenhicken.com/}{Allen Hicken} and \href{http://www.nicoravanilla.com/}{Nico Ravanilla}.

% \item ``Incumbency Advantage and Family Success in Local Elections'' with Sara M. Kerosky.

\end{enumerate}

\subsection*{Working Papers (Completed Draft)}

\begin{enumerate}
\item ``Mine All Mine: Corruption and Electoral Competition'' with Sara M Kerosky.

\item \href{http://polisci2.ucsd.edu/mwdavidson/Davidson-Haim_Buying%20Attention-Campaign%20Advertisements%20and%20Candidate%20Salience.pdf}{``Buying Attention: Campaign Advertisements and Candidate Salience''} with Dotan A. Haim.

\item ``Electoral Institutions, Social Structure and Ethnic Voting''.

\item ``Gendered Speech Under Authoritarian Rule: A Structural Topic Analysis of Women's Speeches in the Vietnam National Assembly'' with \href{http://polisci2.ucsd.edu/pschuler/}{Paul Schuler}.


\item ``Using Networks to Find Better Politicians: Evidence from the Philippines'' with \href{http://cesicruz.com/}{Cesi Cruz}.


\item ``Measuring Implicit Racial Framing in Campaign Advertisements with Automated Text Analysis'' with Jason Wu.
\end{enumerate}

\section*{Grants}
\begin{itemize}
\item \emph{Police-Community Embeddedness in the Philippines.} \$10,000 with Dotan Haim and Matthew Nanes from the \href{http://pdel.ucsd.edu/}{Policy Design and Evaluation Lab}, School of Globab Policy and Strategy, University of California, San Diego.

\item \emph{Remote Sensing and Monitoring Corruption in Developing Democracies.} Frontiers of Innovation Scholar. \$25,000 with Sara Kerosky from the University of California, San Diego. 

\item \emph{Can technology be used to lower the barrier to entry in elections?} \$40,000 with \href{http://cesicruz.com/}{Cesi Cruz} from the \href{http://pdel.ucsd.edu/}{Policy Design and Evaluation Lab}, School of International Relations and Pacific Studies, University of California, San Diego.

\item \emph{Lab Experiments on Caste, Religion and Discrimination}. \$1,500 from the Office on Research and Creative Activities (ORCA), BYU.   
\end{itemize}

\section*{Awards}
\begin{itemize}
  \item Southeast Asia Research Group Young Fellow, 2016. 
\end{itemize}

\begin{itemize}
  \item APSA Southeast Asian Politics Group Best Paper Award, 2015. ``Inducement or Entry Ticket? Broker Networks and Vote Buying in Indonesia'' with \href{https://researchers.anu.edu.au/researchers/aspinall-et}{Edward Aspinall}, \href{http://www.allenhicken.com/}{Allen Hicken} and \href{http://www.albany.edu/rockefeller/faculty_pos_weiss.shtml}{Meredith Weiss}.
\end{itemize}


\section*{Presentations}
\begin{itemize}
  \item American Political Science Association (2014, 2011)
  \item Western Political Science Association (2015, 2014)
  \item Midwest Political Science Association (2015)
\end{itemize}

\section*{Professional Experience}

\begin{itemize}
\item Consultant: World Bank, \emph{Candidate Promises, Citizens Knowledge and Vote-Buying: Experimental Evidence from the Philippines} (2013)
\item Research Assistant:
  \href{http://jhfowler.ucsd.edu/}{James Fowler} (2013-2014),
  \href{http://polisci2.ucsd.edu/snunnari/}{Salvatore Nunnari} (2013),
  \href{http://polisci2.ucsd.edu/cadida/Site/Welcome.html}{Claire
    Adida} (2013)
  and 
  \href{http://fhssfaculty.byu.edu/FacultyPage.aspx?id=jss83}{Joel
    S. Selway} (2009-2011, 2014-2015).
\item Intern, \href{cantwell.senate.gov}{United States Senator Maria
    Cantwell (D)} (2009)

\item Intern, \href{http://www.leg.wa.gov/senate/senators/Pages/roach.aspx}{Washington
    State Senator Pam Roach (R)} (2005).
\end{itemize}

\section*{Technical Skills}
\begin{multicols}{2}
\begin{itemize}
\item R:
\begin{itemize}
  \item \texttt{data.table} -- big data manipulation
  \item \texttt{igraph} -- network analysis
  \item \texttt{caret} -- machine learning
  \item \texttt{tm} -- text mining
\end{itemize}
\item Stata
\item LaTeX
\item Markdown
\item HTML
\end{itemize}
\end{multicols}

\section*{Academic Service}
\begin{itemize}
  \item Co-organizer of UC San Diego \href{http://hng.ucsd.edu/index.html}{Human Nature Group} \hfill 2013 - 2014
  \item UC San Diego Political Science Recruitment Co-chair \hfill 2013
\end{itemize}

\section*{Language}
\begin{itemize}
  \item Tagalog/Filipino (Fluent)
\end{itemize}


\section*{References}
\begin{itemize}
\item \href{jhfowler.ucsd.edu}{James H. Fowler}, Professor, University of California, San Diego
\item \href{http://www.allenhicken.com/}{Allen Hicken}, Professor, University of Michigan
% \item \href{https://sites.google.com/site/joelsawatselway/}{Joel S. Selway}, Assistant Professor, Brigham Young University
\end{itemize}

\bigskip
% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}